---
output:
    md_document:
      variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "tools/README-",
  warning = FALSE
)
```

# carnaval

<!-- badges: start -->
[![Lifecycle: experimental](https://lifecycle.r-lib.org/articles/figures/lifecycle-experimental.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Carnaval is the biggest street feast of Brazil. It happens all over the country in a kaleidoscope of sound and color. One of the forms it takes is the yearly competition between Samba Schools in Rio. The `carnaval` R package provides easy access to both datasets on the competition and color palettes inspired by the Samba Schools.

The package is under development and has these functions:

- get_scores: Obtain scores of samba schools by year, school and/or criterion.

## Installation and loading

Install `carnaval` from [GitHub](https://github.com/IcaroBernardes/carnaval) as follows: 

```{r, eval=FALSE}
if(!require(devtools)) install.packages("devtools")
devtools::install_github("IcaroBernardes/carnaval")
```

## Examples

```{r, warning=FALSE, message=FALSE}
library(carnaval)

# Prints a table that shows the scores of Portela and
# Est치cio de S치 on the parades of 1968 and 1970 on all criterions
get_scores(years = c(1968, 1970), schools = c("portela", "Est치cio de S치"))
```
